---
output: github_document
---


```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```


# LDDMM

An R package for Longitudinal Drift-Diffusion Mixed Models (LDDMM), v0.2.0.

**Authors**: [Giorgio Paulon](https://giorgiopaulon.github.io/), [Abhra Sarkar](https://abhrastat.github.io/)

### Overview

Codes accompanying "Bayesian Semiparametric Longitudinal Drift-Diffusion Mixed Models for Tone Learning in Adults" by Paulon, Llanos, Chandrasekaran, Sarkar.

This package implements a novel generic framework for longitudinal functional mixed models that allows automated assessment of an associated predictor's local time-varying influence. We build on this to develop a novel inverse-Gaussian drift-diffusion mixed model for multi-alternative decision-making processes in longitudinal settings. Our proposed model and associated computational machinery make use of B-spline mixtures, hidden Markov models (HMM) and factorial hidden Markov models (fHMM), locally informed Hamming ball samplers etc. to address statistical challenges.

The main function is `LDDMM`; please see the following vignette for details, as well as the main article:

Paulon, G., Llanos, F., Chandrasekaran, B., Sarkar, A. (2021). [Bayesian semiparametric longitudinal drift-diffusion mixed models for tone learning in adults](https://www.tandfonline.com/doi/abs/10.1080/01621459.2020.1801448?journalCode=uasa20). Journal of the American Statistical Association **116**, 1114-1127

The data included in this package was analyzed in: 

Roark, C. L., Paulon, G., Sarkar, A., Chandrasekaran, B. (2021). [Comparing perceptual category learning across modalities in the same individuals](https://link.springer.com/article/10.3758/s13423-021-01878-0). Psychonomic Bulletin & Review **28**, 898-909

and is available [here](https://osf.io/msnq2/).

### Installation

To install the package in R, first install the `devtools` package, and then use the commands
```{r, eval = FALSE}
library(devtools)
install_github('giorgiopaulon/lddmm')
```
If you are using a Windows machine, you might have to also install and configure `Rtools` using the following [instructions](https://CRAN.R-project.org/bin/windows/Rtools/).

### Usage

The following is a minimal example of a simple model fit. 
For numerical stability, the response times should be provided as the log transform of time (in milliseconds) so that, for most applications, typical values lie in $[0, 10]$. 

```{r, eval = TRUE, results = 'hide', fig.show = 'hide', warning = FALSE, message = FALSE}
# Load libraries
library(RColorBrewer)
library(ggplot2)
library(dplyr)
library(reshape2)
library(latex2exp)
library(lddmm)

theme_set(theme_bw(base_size = 14))
cols <- brewer.pal(9, "Set1")

# Load the data
data('data')

# Descriptive plots
plot_accuracy(data)
plot_RT(data)

# Run the model
hypers <- NULL
hypers$s_sigma_mu <- hypers$s_sigma_b <- 0.1

# Change the number of iterations when running the model
# Here the number is small so that the code can run in less than 1 minute
Niter <- 25
burnin <- 15
thin <- 1
samp_size <- (Niter - burnin) / thin

set.seed(123)
fit <- LDDMM(data = data, 
             hypers = hypers, 
             Niter = Niter, 
             burnin = burnin, 
             thin = thin)

# Plot the results
plot_post_pars(data, fit, par = 'drift')
plot_post_pars(data, fit, par = 'boundary')
```


To extract relevant posterior draws or posterior summaries instead of simply plotting them, one can use the functions `extract_post_mean` or `extract_post_draws`. 
Auxiliary functions that assume constant boundary parameters over time or fix the boundaries to the same level across predictors can be called with the options `boundaries = "constant"` and `boundaries = "fixed"`, respectively.


### Questions or bugs

For bug reporting purposes, e-mail Giorgio Paulon (giorgio.paulon@utexas.edu).

### Citation

Please cite the following publication if you use this package in your research: Paulon, G., Llanos, F., Chandrasekaran, B., Sarkar, A. (2021). [Bayesian semiparametric longitudinal drift-diffusion mixed models for tone learning in adults](https://www.tandfonline.com/doi/abs/10.1080/01621459.2020.1801448?journalCode=uasa20). Journal of the American Statistical Association **116**, 1114-1127